### 2022-08-15 doc/src/CSRs.tex
Add preface and update status of each chapter

\textbf{%
Warning!
This draft specification is likely to change before being accepted as
standard by the {\RISCV} International Association.%
}
\bigskip

@@

Table~\ref{tab:CSRs-M} lists the CSRs added for machine level.

@@

Table~\ref{tab:CSRs-S} lists the supervisor-level CSRs that are added
if the hart implements \mbox{S-mode}.
The functions of these registers all match their machine-level
counterparts.

@@

If a hart implements the Privileged Architecture's hypervisor
extension, then the hypervisor and VS CSRs listed in
Table~\ref{tab:CSRs-hypervisor} are also added.

>>>>

\textbf{%
This chapter is considered stable but could still change before being
ratified as standard by the {\RISCV} International Association.%
}
\bigskip

@@

Table~\ref{tab:CSRs-M} lists the CSRs added for machine level.
Each of these registers is MXLEN bits in size.

@@

Table~\ref{tab:CSRs-S} lists the supervisor-level CSRs that are added
if the hart implements \mbox{S-mode}.
Each of these registers is SXLEN bits in size.
The functions of these registers all match their machine-level
counterparts.

@@

If a hart implements the Privileged Architecture's hypervisor
extension, then the hypervisor and VS CSRs listed in
Table~\ref{tab:CSRs-hypervisor} are also added.
The VS CSRs are all VSXLEN bits wide,
while the hypervisor CSRs are all HSXLEN bits.
(\textit{HSXLEN} is just another name for
SXLEN for hypervisor-extended \mbox{S-mode}).
